Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

In modern CPUs, L1 and L2 caches are traditional N-way set associate caches. That is, the cache is divided into several cache sets, and each set contains several cache lines. The cache line is the atomic unit. As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the following steps.  Given an address, the CPU uses the \textsf{Index} field of the address to locate the cache set that the address should reside in. After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line. If the CPU can locate a cache line with the same tag and the valid bit is set, then a cache hit occurs. The CPUs use a similar process to manage the main memory. The main memory is divided into many units called pages. As shown in Figure~\ref{fig:memory_address},
the translation process keeps the bottom bits same while using the top bits to map the Physical Page Numbers to Virtual Page Numbers.

>>>>

In modern CPUs, L1 and L2 caches are traditional N-way set associate caches. That is, the cache is divided into several cache sets, and each set contains several cache lines. The cache line is the atomic unit. As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the following steps.  Given an address, the CPU uses the \textsf{Index} field of the address to locate the cache set that the address should reside in. After that, it uses the \textsf{Tag} field to match every cache line inside the set line. If the CPU can locate a cache line with the same tag and the valid bit is set, then a cache hit occurs. The CPU uses a similar process to manage the main memory. The main memory is divided into many units called pages. As shown in Figure~\ref{fig:memory_address},
the translation process keeps the bottom bits same while using the top bits to map the Physical Page Numbers to Virtual Page Numbers.
